---
title: "p1"
output: html_document
date: "2024-12-03"
---

```{r include=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(SemiPar)
library(ggridges)
library(patchwork)
library(forcats)
library(modelr) 
library(mgcv)

#R figure settings
knitr::opts_chunk$set(
  fig.width = 9,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r}
weather_df =
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"),
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_N
Y"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
boot_strap_results = weather_df |> 
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin, data = df)),
   results = map(models, ~ {glance_v = broom::glance(.x) 
      tidy_v = broom::tidy(.x) |>
        filter(term != "(Intercept)") |>
        pull(estimate)
      logb0_logb1 = log(tidy_v[1] * tidy_v[2])  
      tibble(
        r_squared = glance_v$r.squared,
        logb0_logb1 = logb0_logb1
      )})) |>
  select(results) |>
  unnest(results)

ggplot(bootstrap_results, aes(x = r_squared)) +
  geom_density() +
  labs(title = "r^2 distribution",
       x = "r^2", 
       y = "density") 

conf_intervals = bootstrap_results |>
  summarize(rsqured_ci = quantile(r_squared, probs = c(0.025, 0.975))#,
    #logb0_logb1_ci = quantile(logb0_logb1, probs = c(0.025, 0.975))
  ) |>
  knitr::kable()



```

sim_df_nonconst |>
  modelr::bootstrap(n = 1000) |>
  mutate(
    models = map(strap, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |>
  select(-strap, -models) |>
  unnest(results) |>
  group_by(term) |>
  summarize(boot_se = sd(estimate))
  
  


nyc_airbnb |>
  filter(borough == "Manhattan") |>
  modelr::bootstrap(n = 1000) |>
  mutate(
    models = map(strap, \(df) lm(price ~ stars + room
_type, data = df)),
    results = map(models, broom::tidy)) |>
  select(results) |>
  unnest(results) |>
  filter(term == "stars") |>
  ggplot(aes(x = estimate)) + geom_density()