---
title: "p8105_hw6_lk2776"
output: github_document
date: "2024-12-02"
---

```{r include=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(SemiPar)
library(ggridges)
library(patchwork)
library(forcats)
library(modelr) 
library(mgcv)

#R figure settings
knitr::opts_chunk$set(
  fig.width = 9,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## problem 2
```{r}
#problem2
data = read_csv("./data/homicide-data.csv", na=c("Unknown",".",""), ) |>
  janitor::clean_names() |>
  drop_na() |>
  mutate(city_state = paste(city, state, sep="_"), 
         status = if_else(
           disposition %in% c("Closed without arrest", "Open/No arrest"), "1", "0")) |>
 filter(!city_state %in% c("Tulsa_AL","Dallas_TX","Phoenix_AZ","Kansas City_MO")) |>
  filter(victim_race %in% c("White","Black")) |>
  mutate(victim_age = as.numeric(victim_age), 
         status = as.numeric(status))

```

```{r}
#baltimore logistic
baltimore_data = data |>
  filter(city_state == "Baltimore_MD") 

fit_logistic =
  baltimore_data |>
  glm(status ~ victim_age + victim_race + victim_sex, data = _, family = binomial()) |>
  broom::tidy(conf.int=TRUE) |>
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) |>
  select(term, log_OR = estimate, OR, conf.low,conf.high,p.value) |>
  filter(term == "victim_sexMale")
  
#fit_logistic |> knitr::kable()

```

```{r}
#all cities - fit logistic
all_cities_fit_logistic = data |> 
  group_by(city_state) |>
  nest() |>
  mutate(models = map(data, \(df) glm(status ~ victim_age + victim_race + victim_sex, data = df, family = binomial())),
  results = map(models, broom::tidy,conf.int=TRUE)) |>
  select(-data, -models) |>
  unnest(results) |>
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) |>
  select(term, log_OR = estimate, OR, conf.low,conf.high,p.value) |>
  filter(term == "victim_sexMale") 

#all_cities_fit_logistic |> knitr::kable()
  
```

The below plot shows gender based differences across city_ state in resolving the crimes. Male victim crimes are more likely to be resolved from fresno_CA to SanBernardino_CA (left to right direction) compared to female victim crimes. 
```{r}

all_cities_fit_logistic |>
 # mutate(city_state = fct_reorder(city_state,OR)) |> #not working
ggplot(aes(x= reorder(city_state,OR), y = OR)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 80, hjust
= 1))+
  geom_errorbar(aes(ymin=conf.low, ymax = conf.high), color = "orange") +
  labs(
    title = "OR across Cities, States",
    x = "City, State",
    y = "OR"
  )
  
```

## problem3 

The modeling process for the initial analysis involves nesting models: Simple regression model is fitted using babysex, bhead, and blength as predictors. A full model, which includes additonal predictors, is then fitted, and the significance of the models using ANova. Since the anova values is less than 0.05, the full model explains more variation. Homoskedasticity, linearity and presence of outliers can be observed in the residulas vs fitted values plot. Two other models are compared with full model using cross validation. The RMSE for full models is lower than for the two other models, making it the preferred model. 


```{r}
bwt_data = read_csv("./data/birthweight.csv", na=c(" ",".","")) |>
  janitor::clean_names() |>
  drop_na() |>
  mutate(
    babysex = as.factor(babysex),
    malform = as.factor(malform),
    frace = as.factor(frace),
    mrace = as.factor(mrace)
  )
#str(bwt_data)

```

```{r}
#model 1
#nested model process of selecting variables 
simple_model_1 = lm(bwt ~ babysex + bhead + blength, data = bwt_data) #baby's variables

full_model_1 = lm(bwt ~ babysex + bhead + blength+ delwt + fincome + frace + gaweeks + malform +
              mrace + pnumlbw + smoken + wtgain, data = bwt_data) 

anova(simple_model_1, full_model_1)|>
  broom::tidy() #p-value less than 0.05 

bwt_data = bwt_data |>
  add_predictions(full_model_1) |> #pred
  add_residuals(full_model_1) #resid

bwt_data |> 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE,color="red" ) #methods 1
  labs(
    title = "Predictions vs Residuals",
    x = "Predictions",
    y = "Residuals"
  ) 

```

```{r}
#main effects
model_2 = lm(bwt ~  blength + gaweeks, data = bwt_data)
model_2 |> 
  broom::tidy() |>
  select(term, estimate, p.value) 

#main effects + interactions
model_3 = lm(bwt ~ bhead * blength * babysex, data = bwt_data)

model_3 |> 
  broom::tidy() |>
  select(term, estimate, p.value) 
```


```{r}
cv_df = crossv_mc(bwt_data, 100) |>
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
  
cv_df =
  cv_df |>
  mutate(
    full_model_1_b  = map(train, \(df) lm(bwt ~ babysex + bhead + blength+ delwt + fincome + frace + gaweeks + malform +
              mrace + pnumlbw + smoken + wtgain, data = df)),
    model_2_b  = map(train, \(df) lm(bwt ~  blength + gaweeks, data = df)),
    model_3_b  = map(train, \(df) lm(bwt ~ bhead * blength * babysex, data = df))) |>
  mutate(
    rmse_full_model = map2_dbl(full_model_1_b, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_mode_l2 = map2_dbl(model_2_b, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_model_3 = map2_dbl(model_3_b, test, \(mod, df) rmse(model = mod, data = df)))


cv_df |>
  select(starts_with("rmse")) |>
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") |>
  mutate(model = fct_inorder(model)) |>
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(title = "RMSE across Models", x = "Model", y = "RMSE")
```

## problem1


```{r}
weather_df =
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"),
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_N
Y"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())


```

```{r}
boot_strap_results = weather_df |> 
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin, data = df)),
   results = map(models, \(model) {glance_v = broom::glance(model) 
      tidy_v = broom::tidy(model) |>
        filter(term != "(Intercept)") |>
        pull(estimate)
      logb0_logb1 = log(tidy_v[1] * tidy_v[2])  
      tibble(
        r_squared = glance_v$r.squared,
        logb0_logb1 = logb0_logb1
      )})) |>
  select(results) |>
  unnest(results)
```


```{r}
boot_strap_results |>
  ggplot(aes(x = r_squared)) +
  geom_density() +
  labs(title = "r^2 distribution",
       x = "r^2", 
       y = "density") 

conf_intervals = boot_strap_results |>
  summarize(rsqured_ci = quantile(r_squared, probs = c(0.025, 0.975))
  ) 
conf_intervals

```


